Causal Forest Approach for Site-specific Input Management via On-farm Precision Experimentation

### 2022-02-08 Codes/PrepareResults.rmd
1. position of R2 labels are changed and the figure height increased to 7.5 2. minor changes in manuscript

```{r}
fig_y_optN <-
  rmse_y_all[Method %in% c("RF", "BRF", "CNN")] %>%
  ggplot(aes(x = rmse_y, y = rmse_optN)) +
  geom_point(size = 0.5) +
  facet_grid(Model ~ Method) +
  # geom_smooth(method='lm', se=FALSE,  aes(colour="Regression line"), size=1) +
  # scale_colour_manual(values= "red") +
  geom_smooth(method = "lm", se = FALSE, color = "red", size = 1) +
  stat_regline_equation(
    label.x = 2150, label.y = 85,
    aes(label = ..rr.label..)
  ) +
  guides(
    fill = guide_legend(keywidth = 1, keyheight = 1),
    linetype = guide_legend(keywidth = 3, keyheight = 1),
    colour = guide_legend(keywidth = 3, keyheight = 1)
  ) +
  labs(y = " RMSE of EONR Estimation (kg/ha)") +
  labs(x = " RMSE of Yield Prediction (kg/ha)") +
  theme_few() +
  theme(
    strip.text.x = element_text(size = 12, face = "bold"),
    strip.text.y = element_text(size = 12, face = "bold"),
    legend.title = element_blank(),
    legend.text = element_text(size = 12, face = "bold"),
    legend.position = "bottom"
  ) +
  theme_figure

>>>>

```{r}
fig_y_optN <-
  rmse_y_all[Method %in% c("RF", "BRF", "CNN")] %>%
  ggplot(aes(x = rmse_y, y = rmse_optN)) +
  geom_point(size = 0.5) +
  facet_grid(Model ~ Method) +
  # geom_smooth(method='lm', se=FALSE,  aes(colour="Regression line"), size=1) +
  # scale_colour_manual(values= "red") +
  geom_smooth(method = "lm", se = FALSE, color = "red", size = 0.7) +
  stat_regline_equation(
    label.x = 2050, label.y = 90,
    aes(label = ..rr.label..),
    size = 3
  ) +
  guides(
    fill = guide_legend(keywidth = 1, keyheight = 1),
    linetype = guide_legend(keywidth = 3, keyheight = 1),
    colour = guide_legend(keywidth = 3, keyheight = 1)
  ) +
  ylim(NA, 95) +
  labs(y = " RMSE of EONR Estimation (kg/ha)") +
  labs(x = " RMSE of Yield Prediction (kg/ha)") +
  theme_few() +
  theme(
    strip.text.x = element_text(size = 12, face = "bold"),
    strip.text.y = element_text(size = 12, face = "bold"),
    legend.title = element_blank(),
    legend.text = element_text(size = 12, face = "bold"),
    legend.position = "bottom"
  ) +
  theme_figure

### 2022-02-08 Writing/manuscript_cea.rmd
minor changes in manuscript
1. position of R2 labels are changed and the figure height increased to 7.5 2. minor changes in manuscript

\begin{equation}
\hat{N}^{opt}_{i} = \operatorname*{argmax}_{N}(p \hat{g}_m(N, \mathbf{\Omega_{i}}) - w N), (\#eq:eqn8)
\end{equation}

@@

```{r plot-y-optN, fig.width=7, fig.height=7, fig.cap = "The relationship in the performance between EONR estimation and yield prediction by ML methods and modeling scenarios"}
fig_y_optN
```

>>>>

\begin{equation}
\hat{N}^{opt}_{i} = \operatorname*{argmax}_{N}(p \cdot\hat{g}_m(N, \mathbf{\Omega_{i}}) - w \cdot N), (\#eq:eqn8)
\end{equation}

@@

```{r plot-y-optN, fig.width=7, fig.height=7.5, fig.cap = "The relationship in the performance between EONR estimation and yield prediction by ML method and modeling scenario"}
fig_y_optN
```
